Efficient implementation of kernel filtering

### 2007-06-25 article/Article.tex
Mean working on 2D and 3D images.
darcs-hash:20070625033126-fafb9-b47ae2488befbccd4fa7277a1a3ce5329088fcba.gz

\subsection{Rank and mean filters -- fastRankMean}
The {\em fastRankMean} packge using the sliding window method to
implement rank and mean filters for arbitary kernel shapes. It also
uses line versions of these kernels to provide a ``separable rank''
filter -- an fast approximation to a real rank filter as discussed in
Section \ref{sect:rank}. There are also a number of filters that
accept a mask input and return the rank or mean value of the
intersection of kernel and mask. These are experimental and haven't
been thoroughly tested.
\section{Performance}
\subsection{Box Convolution}
The relative times for optimized and standard convolution are shown in
Table \ref{tab:perfBoxConv}, and demonstrate significantly improved
performance sor kernel radii greater than 3. The execution times of
box convolution should be relatively constant with kernel size, but an
obvious increase is clear. This is attributable to the process of
dealing with the boundary conditions, which utilizes shaped
neighborhood filters. This aspect of the implementation needs further work

\begin{table}[htbp]
\centering
\begin{tabular}{ccc}
\hline
Size  &  Direct &  Box \\
\hline
\hline
1   &    0.0109048   &    0.0233631 \\
2   &    0.022008    &    0.0245971 \\
3   &    0.0434739   &    0.0263161 \\
4   &    0.0780701   &    0.0283061 \\
5   &    0.129174    &    0.0310797 \\
6   &    0.199876    &    0.0344833 \\
7   &    0.289754    &    0.0382629 \\
8   &    0.407095    &    0.043121 \\
9   &    0.552862    &    0.0489335 \\
10  &    0.728667    &    0.0555441 \\
15  &    2.17149     & 0.107776 \\
20  &    4.83458     & 0.199508 \\
25  &    9.12699     & 0.372637 \\
\hline

\end{tabular}
\caption{Execution times for direct and box convolution implementations applied to the $256 \times 256$ cthead image.\label{tab:perfBoxConv}}
\end{table}

>>>>

\subsection{Rank and mean filters -- fastRankMean}
The {\em fastRankMean} packge using the sliding window method to
implement rank and mean filters for arbitary kernel shapes. It also
uses line versions of these kernels to provide a ``separable rank''
filter -- an fast approximation to a real rank filter as discussed in
Section \ref{sect:rank}. There are also a number of filters that
accept a mask input and return the rank or mean value of the
intersection of kernel and mask. These are experimental and haven't
been thoroughly tested.

\subsection{Rectangular convolution -- boxConvolution}
The {\em boxConvolution} uses the accumulation method described in
Section \ref{sect:meanVar} to implement rectangular mean and variance
computations. The filters implement different boundary conditions to
{\em itkMeanImageFilter}, with the mean of the kernel inside the image
being computed.

\section{Performance}
\subsection{Morpholgy}

\subsection{Rank and Mean filters}

\subsection{Box Convolution}
The relative times for optimized and standard convolution are shown in
Table \ref{tab:perfBoxConv}, and demonstrate significantly improved
performance for kernel radii greater than 2. The times indicate the
theoretical prediction that the complexity of the algorithm is
independent of kernel size.
\begin{table}[htbp]
\centering
\begin{tabular}{ccc}
\hline
Size  &  Direct &  Box \\
1  &     0.014205    &    0.0256313 \\
2  &     0.0355665   &    0.0257389 \\
3  &     0.0507895   &    0.0194342 \\
4  &     0.0745054   &    0.0152253 \\
5  &     0.124225    &    0.0149731 \\
6  &     0.187713    &    0.0149678 \\
7  &     0.27351     &    0.0152494 \\
8  &     0.411708    &    0.0155574 \\
9  &     0.518938    &    0.0156469 \\
10 &     0.682868    &    0.0158462 \\
15  &    2.02712     &    0.0165146 \\
20  &    4.46925     &    0.0176763 \\
25  &    8.43348      & 0.0182798 \\
\hline
\hline
\end{tabular}
\caption{Execution times for direct and box convolution implementations applied to the $256 \times 256$ cthead image on a ??.\label{tab:perfBoxConv}}
\end{table}
